Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-12-06 Submission.Rmd
hudson dunn bros

abstract: |
  Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands. The current study documents variability in ratings of O\*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes. We additionally explore the potential moderating role of resources on these relationships. Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful. Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships. These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.

keywords         : "O*NET, challenge-hindrance framework, job demands-resources, job characteristics"
wordcount        : "4,942"

@@

```{r demos, eval=FALSE}

>>>>

abstract: |
 **Purpose**: Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands. The purpose of this paper was to examine 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association with positive and negative outcomes, and 3) the potential buffering effect of resources on the relationships between demands and negative work outcomes. **Design/methodology/approach**: A sample of 568 respondents recruited from Prolific completed an online survey. They were asked to think only about their primary job, and each administered survey branched content dependent on whether this job could be described as consisting of the different O\*NET job characteristics. They subsequently rated level of resource, challenge, or hindrance. **Findings**: Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly interpreted as resourceful. Furthermore, greater experienced resources moderate the challenge–engagement relationship as well as the hindrance-stress and hindrance–burnout relationships. **Originality/value**: We utilized a diverse sample of employees across industries who responded to items derived from O*NET specifications. O*NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations. We also explored characteristics at a higher level of aggregation (retaining O*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them. 
keywords         : "O*NET, challenge-hindrance framework, job demands-resources, job characteristics"
wordcount        : "4,942"

@@

```{r demos}
